old snippets

### 2024-09-12 manuscript/manuscript.qmd
trying to reestablish git

The goal of this study was to investigate how exposure to two types of adversity---material deprivation and threat---in adulthood is associated to inhibition and attention shifting ability.
Participants completed two inhibition tasks, three attention shifting tasks, and one basic processing speed task.
First, we used DDM to

>>>>

The goal of this study was to XXXinvestigate how exposure to two types of adversity---material deprivation and threat---in adulthood is associated to inhibition and attention shifting ability.
Participants completed two inhibition tasks, three attention shifting tasks, and one basic processing speed task.
First, we used DDM to
